Modeling Two-Dimensional Vesicle Hydrodynamics with Hydrophobic Attraction Potential Simulations

### 2021-05-04 doc/main_jfm.tex
RJR mods
adding some texts

\usepackage{graphicx}
%\usepackage{epstopdf,epsfig}
\usepackage{newtxtext}
\usepackage{newtxmath}
\usepackage{natbib}
\usepackage{hyperref}
\hypersetup{
    colorlinks = true,
    urlcolor   = blue,
    citecolor  = black,
}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}
\newcommand{\RomanNumeralCaps}[1]
\linenumbers

@@

\subsection{Single Particle Validations}
Jeffery orbits for single elliptic particle under a shear flow.

@@

\section{Appendices}
The stress ${\bf T}$ contains the gradient of the double layer potential. This 
introduces an inherent difficulty in evaluating stress on the boundary.
To overcome the difficulty of evaluation on $\Sigma_p$, for instance, we decompose $u$ into singular and nonsingular parts:
\begin{equation}
u = u_p + v_p
\end{equation}
where  
\begin{equation}
u_p(x) = \int_{\Sigma_p} \frac{\partial G(x,y)}{\partial \nu} \eta(y) \,\dif S(y).
\end{equation}
It turns out that the contribution to the force and torque coming from the singular
part vanishes. In particular, we will prove the identity
\begin{equation}
\label{eq:recipforcetorque}
F_p + iG_p= \int_{\Sigma_p} ({\bf I}+i{\bf X})J_{p} \,\dif S
\end{equation}
where
 \begin{equation}
\label{eq:jumpstress1}
J_{p} &= 2\rho^{-1} \eta  v_p \nu 
+ 2\rho \nabla \eta \cdot \tau_i(\nabla v_p \cdot \tau_i \nu -  \nabla v_p \cdot \nu \tau_i).
\end{equation}
Here $\nu$ is the unit normal, $\{\tau_i\}_{i=1}^2$ are orthonormal tangent vectors,
and ${\bf X}$ is the skew symmetric matrix with axial vector $x$, i.e.
\[X_{ij} = \varepsilon_{ikj}x_k,\quad {\bf X}v = x\times v\]
where $\boldsymbol{\varepsilon}$ is the third-order alternating tensor.
We employ the Einstein summation convention and use complex vectors to streamline the presentation, $i^2 = -1$.

@@

Using Lemma \ref{eq:stress_div_lemma}, we will establish that
\begin{equation}
  \label{eq:prejump}
  F_p + i G_p = \int_{\Sigma_p}  ({\bf U}_2\nu)^+ - ({\bf U}_2\nu)^-\,\dif S
\end{equation}
where ${\bf U}_j = ({\bf I} + i {\bf X}){\bf T}_j$ for $j = 1, 2, 3.$
The stress ${\bf U}_2$ has a jump discontinuity at $\Sigma_p.$
The plus and minus superscripts denote
the limit taken along points in $U_p^c$ and along points in $U_p$
respectively.
${\bf U}_1$ and ${\bf U}_3$ are real-analytic in a neighborhood of $\overline{U_p}$
and have no jump-discontinuity at $\Sigma_p$.
To derive \eqref{eq:prejump}, we expand
\begin{align*}
  F_p + i G_p
  &= \int_{\Sigma_p} {\bf T} \nu + ix \times {\bf T} \nu \,\dif S \\
  &= \int_{\Sigma_p}  {\bf U}_1\nu  + ({\bf U}_2\nu)^+ + {\bf U}_3\nu\,\dif S
\end{align*}
The function $u_p$ is real-analytic and
$\nabla \cdot {\bf U}_1 = 0$ throughout $\mathbb{R}^n \setminus U_p$.
By the divergence theorem, we get
\begin{equation*}
  \int_{\Sigma_p}  {\bf U}_1 \nu\,\dif S
  = \int_{\mathrr{R}^n \setminus U_p} \nabla \cdot {\bf U}_1 \,dx = 0.
\end{equation*}
Next, $v_p$ is real-analytic and
$\nabla \cdot {\bf U}_3 = 0$ in $U_p$. Therefore
\begin{equation*}
  \int_{\Sigma_p}  {\bf U}_3 \nu\,\dif S
  = -\int_{U_p} \nabla \cdot {\bf U}_3 \,dx = 0.
\end{equation*}
Finally, $\nabla \cdot {\bf U}_2= 0$ in $U_p$. This gives
\[
0 = -\int_{U_p} \nabla \cdot {\bf U}_2 \,dx = \int_{\Sigma_p}  ({\bf U}_2 \nu)^-\,\dif S.
\]
Combining the last four equations give \eqref{eq:prejump}.

\begin{proof}[Proof of \eqref{eq:recipforcetorque}]
  The main ingredients of the proof are the jump relations
  for $u_p$. For $x_0 \in \Sigma_p$,
  \begin{enumerate}
  \item $ \lim_{x \to x_0^\pm } u_p(x) = \pm\frac{1}{2}\eta(x_0) + (D\eta)(x_0)$
  \item $ \lim_{x \to x_0^+ } (\nabla u_p \cdot \nu) (x) = \lim_{x \to x_0^-} (\nabla u \cdot \nu)(x)$
  \end{enumerate}
  Furthermore,
  combining 1. and 2. give
  \begin{align*}
    \nabla u_p^+ - \nabla u_p^-
    &= \nabla (u_p^+ - u_p^-) \cdot t_i t_i +  (\nabla  u_p^+\cdot \nu  - \nabla u_p^- \cdot \nu) \nu\\
    &= \nabla \eta \cdot \tau_i \tau_i
  \end{align*}
  where $\{\tau_i\}_{i=1}^n$ are an orthonormal tangent vectors.
  We can use these relationships to derive an expression for the jump in
  normal stress.
  \begin{align*}
    &({\bf T}_2\nu)^+ - ({\bf T}_2\nu)^-
    \\
    &= 2\rho^{-1} u_p^+v_p \nu + 2\rho \nabla u_p^+ \cdot \nabla v_p \nu
    - 2 \rho \nabla u_p^+  \nabla v_p \cdot \nu
    - 2 \rho \nabla v_p  \nabla u_p^+ \cdot \nu\\
    &-2\rho^{-1} u_p^-v_p \nu - 2\rho \nabla u_p^- \cdot \nabla v_p \nu
    + 2 \rho \nabla u_p^-  \nabla v_p \cdot \nu
    + 2 \rho \nabla v_p  \nabla u_p^- \cdot \nu\\
    &= 2\rho^{-1} \eta v_p \nu + 2\rho \nabla \eta \cdot \tau_i \tau_i \cdot \nabla v_p \nu
    - 2\rho \nabla \eta \cdot \tau_i \tau_i \nabla v_p \cdot \nu + 0\\
    &= J_p.
  \end{align*}

>>>>

\usepackage{graphicx}
%\usepackage{epstopdf,epsfig}
\usepackage{newtxtext}
\usepackage{newtxmath}
\usepackage{natbib}
\usepackage{hyperref}
\usepackage{mathtools}
\usepackage{commath}
\hypersetup{
    colorlinks = true,
    urlcolor   = blue,
    citecolor  = black,
}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}
\newcommand{\RomanNumeralCaps}[1]
\linenumbers

@@

\subsection{Single Particle Validations}

The first study of the proposed numerical algorithm is the Jeffery orbits of single ellipsoidal particle under a shear flow. A particle is initially placed with its center of mass fixed at the origin and the angle between the major axis and the x-axis is $\chi = 90^\circ$. Based on the theoretical Jeffery orbits,

\begin{equation}
\chi = \tan^{-1}\frac{a}{b}\tan \frac{ab \dot\gamma t}{a^2+b^2}
\end{equation}
%
where $a$, $b$ are semi-major and semi-minor axes, $\dot\gamma$ is the shear rate, and the test aspect ration of the particle is $2$. Figure~\ref{figure1} shows that the proposed integral equation method has a perfect agreement with the theoretical result from Jeffery orbits.

\begin{figure}[h]
\begin{center}
\includegraphics[width=0.5\textwidth]{JefferyOrbit.eps}
\end{center}
  \caption{Comparison of the target angle $\chi(t)$ versus time $t$ between the theoretical Jeffery orbit and the intergal equation method.
  }
    \label{figure1}
\end{figure}

@@

\section{Appendices}
The stress ${\bf T}$ contains the gradient of the double layer potential. This 
introduces an inherent difficulty in evaluating stress on the boundary.
To overcome the difficulty of evaluation on $\Sigma_p$, for instance, we decompose $u$ into singular and nonsingular parts:
\begin{equation}
u = u_p + v_p
\end{equation}
where  
\begin{equation}
u_p(x) = \int_{\Sigma_p} \frac{\partial G(x,y)}{\partial \nu} \eta(y) \,\dif S(y).
\end{equation}
It turns out that the contribution to the force and torque coming from the singular
part vanishes. In particular, we will prove the identity
\begin{equation}
\label{eq:recipforcetorque}
F_p + iG_p= \int_{\Sigma_p} \gamma ({\bf I}+i{\bf X})J_{p} \,\dif S
\end{equation}
where
 \begin{equation}
\label{eq:jumpstress1}
J_{p} = 2\rho^{-1} \eta  v_p \nu 
+ 2\rho \nabla \eta \cdot \tau_i(\nabla v_p \cdot \tau_i \nu -  \nabla v_p \cdot \nu \tau_i).
\end{equation}
Here $\nu$ is the unit normal, $\{\tau_i\}_{i=1}^2$ are orthonormal tangent vectors,
and ${\bf X}$ is the skew symmetric matrix with axial vector $x$, i.e.
\[X_{ij} = \varepsilon_{ikj}x_k,\quad {\bf X}v = x\times v\]
where $\boldsymbol{\varepsilon}$ is the third-order alternating tensor.
We employ the Einstein summation convention and use complex vectors to streamline the presentation, $i^2 = -1$.

@@

Using Lemma \ref{eq:stress_div_lemma}, we will establish that
\begin{equation}
  \label{eq:prejump}
  F_p + i G_p = \gamma \int_{\Sigma_p}  ({\bf U}_2\nu)^+ - ({\bf U}_2\nu)^-\,\dif S
\end{equation}
where ${\bf U}_j = ({\bf I} + i {\bf X}){\bf T}_j$ for $j = 1, 2, 3.$
The stress ${\bf U}_2$ has a jump discontinuity at $\Sigma_p.$
The plus and minus superscripts denote
the limit taken along points in $U_p^c$ and along points in $U_p$
respectively.
${\bf U}_1$ and ${\bf U}_3$ are real-analytic in a neighborhood of $\overline{U_p}$
and have no jump-discontinuity at $\Sigma_p$.
To derive \eqref{eq:prejump}, we expand
\begin{align*}
  F_p + i G_p
  &= \gamma \int_{\Sigma_p} {\bf T} \nu + ix \times {\bf T} \nu \,\dif S \\
  &= \gamma \int_{\Sigma_p}  {\bf U}_1\nu  + ({\bf U}_2\nu)^+ + {\bf U}_3\nu\,\dif S
\end{align*}
The function $u_p$ is real-analytic and
$\nabla \cdot {\bf U}_1 = 0$ throughout $\mathbb{R}^n \setminus U_p$.
By the divergence theorem, we get
\begin{equation*}
  \int_{\Sigma_p}  {\bf U}_1 \nu\,\dif S
  = \int_{\mathbb{R}^n \setminus U_p} \nabla \cdot {\bf U}_1 \,dx = 0.
\end{equation*}
Next, $v_p$ is real-analytic and
$\nabla \cdot {\bf U}_3 = 0$ in $U_p$. Therefore
\begin{equation*}
  \int_{\Sigma_p}  {\bf U}_3 \nu\,\dif S
  = -\int_{U_p} \nabla \cdot {\bf U}_3 \,dx = 0.
\end{equation*}
Finally, $\nabla \cdot {\bf U}_2= 0$ in $U_p$. This gives
\[
0 = -\int_{U_p} \nabla \cdot {\bf U}_2 \,dx = \int_{\Sigma_p}  ({\bf U}_2 \nu)^-\,\dif S.
\]
Combining the last four equations give \eqref{eq:prejump}.

\begin{proof}[Proof of \eqref{eq:recipforcetorque}]
  The main ingredients of the proof are the jump relations
  for $u_p$. For $x_0 \in \Sigma_p$,
  \begin{enumerate}
  \item $ \lim_{x \to x_0^\pm } u_p(x) = \pm\frac{1}{2}\eta(x_0) + (D\eta)(x_0)$
  \item $ \lim_{x \to x_0^+ } (\nabla u_p \cdot \nu) (x) = \lim_{x \to x_0^-} (\nabla u \cdot \nu)(x)$
  \end{enumerate}
  Furthermore,
  combining (i) and (ii) gives
  \begin{align*}
    \nabla u_p^+ - \nabla u_p^-
    &= \nabla (u_p^+ - u_p^-) \cdot t_i t_i +  (\nabla  u_p^+\cdot \nu  - \nabla u_p^- \cdot \nu) \nu\\
    &= \nabla \eta \cdot \tau_i \tau_i
  \end{align*}
  where $\{\tau_i\}_{i=1}^n$ are an orthonormal tangent vectors.
  We can use these relationships to derive an expression for the jump in
  normal stress.
  \begin{align*}
    &({\bf T}_2\nu)^+ - ({\bf T}_2\nu)^-
    \\
    &= 2\rho^{-1} u_p^+v_p \nu + 2\rho \nabla u_p^+ \cdot \nabla v_p \nu
    - 2 \rho \nabla u_p^+  \nabla v_p \cdot \nu
    - 2 \rho \nabla v_p  \nabla u_p^+ \cdot \nu\\
    &-2\rho^{-1} u_p^-v_p \nu - 2\rho \nabla u_p^- \cdot \nabla v_p \nu
    + 2 \rho \nabla u_p^-  \nabla v_p \cdot \nu
    + 2 \rho \nabla v_p  \nabla u_p^- \cdot \nu\\
    &= 2\rho^{-1} \eta v_p \nu + 2\rho \nabla \eta \cdot \tau_i \tau_i \cdot \nabla v_p \nu
    - 2\rho \nabla \eta \cdot \tau_i \tau_i \nabla v_p \cdot \nu + 0\\
    &= J_p.
  \end{align*}
